Adaptive broadcast tree for multicores

### 2013-06-07 graphs/visu_ziger_badtree.tex
New visualization applied to all combinations of machines and topologies except for rings

\draw[fill,color=red!10] (-3cm,7.500000mm) rectangle (30cm,-7.500000mm);
\node at (0mm,0mm) {core 00};
\draw[color=black!30] (20mm,0mm) -- (30cm,0mm);
\draw[fill,color=red!10] (-3cm,22.500000mm) rectangle (30cm,7.500000mm);
\node at (0mm,15mm) {core 01};
\draw[color=black!30] (20mm,15mm) -- (30cm,15mm);
\draw[fill,color=red!10] (-3cm,37.500000mm) rectangle (30cm,22.500000mm);
\node at (0mm,30mm) {core 02};
\draw[color=black!30] (20mm,30mm) -- (30cm,30mm);
\draw[fill,color=red!10] (-3cm,52.500000mm) rectangle (30cm,37.500000mm);
\node at (0mm,45mm) {core 03};
\draw[color=black!30] (20mm,45mm) -- (30cm,45mm);
\draw[fill,color=red!10] (-3cm,67.500000mm) rectangle (30cm,52.500000mm);
\node at (0mm,60mm) {core 04};
\draw[color=black!30] (20mm,60mm) -- (30cm,60mm);
\draw[fill,color=red!10] (-3cm,82.500000mm) rectangle (30cm,67.500000mm);
\node at (0mm,75mm) {core 05};
\draw[color=black!30] (20mm,75mm) -- (30cm,75mm);
\draw[fill,color=green!10] (-3cm,97.500000mm) rectangle (30cm,82.500000mm);
\node at (0mm,90mm) {core 06};
\draw[color=black!30] (20mm,90mm) -- (30cm,90mm);
\draw[fill,color=green!10] (-3cm,112.500000mm) rectangle (30cm,97.500000mm);
\node at (0mm,105mm) {core 07};
\draw[color=black!30] (20mm,105mm) -- (30cm,105mm);
\draw[fill,color=green!10] (-3cm,127.500000mm) rectangle (30cm,112.500000mm);
\node at (0mm,120mm) {core 08};
\draw[color=black!30] (20mm,120mm) -- (30cm,120mm);
\draw[fill,color=green!10] (-3cm,142.500000mm) rectangle (30cm,127.500000mm);
\node at (0mm,135mm) {core 09};
\draw[color=black!30] (20mm,135mm) -- (30cm,135mm);
\draw[fill,color=green!10] (-3cm,157.500000mm) rectangle (30cm,142.500000mm);
\node at (0mm,150mm) {core 10};
\draw[color=black!30] (20mm,150mm) -- (30cm,150mm);
\draw[fill,color=green!10] (-3cm,172.500000mm) rectangle (30cm,157.500000mm);
\node at (0mm,165mm) {core 11};
\draw[color=black!30] (20mm,165mm) -- (30cm,165mm);
\draw[fill,color=blue!10] (-3cm,187.500000mm) rectangle (30cm,172.500000mm);
\node at (0mm,180mm) {core 12};
\draw[color=black!30] (20mm,180mm) -- (30cm,180mm);
\draw[fill,color=blue!10] (-3cm,202.500000mm) rectangle (30cm,187.500000mm);
\node at (0mm,195mm) {core 13};
\draw[color=black!30] (20mm,195mm) -- (30cm,195mm);
\draw[fill,color=blue!10] (-3cm,217.500000mm) rectangle (30cm,202.500000mm);
\node at (0mm,210mm) {core 14};
\draw[color=black!30] (20mm,210mm) -- (30cm,210mm);
\draw[fill,color=blue!10] (-3cm,232.500000mm) rectangle (30cm,217.500000mm);
\node at (0mm,225mm) {core 15};
\draw[color=black!30] (20mm,225mm) -- (30cm,225mm);
\draw[fill,color=blue!10] (-3cm,247.500000mm) rectangle (30cm,232.500000mm);
\node at (0mm,240mm) {core 16};
\draw[color=black!30] (20mm,240mm) -- (30cm,240mm);
\draw[fill,color=blue!10] (-3cm,262.500000mm) rectangle (30cm,247.500000mm);
\node at (0mm,255mm) {core 17};
\draw[color=black!30] (20mm,255mm) -- (30cm,255mm);
\draw[fill,color=orange!10] (-3cm,277.500000mm) rectangle (30cm,262.500000mm);
\node at (0mm,270mm) {core 18};
\draw[color=black!30] (20mm,270mm) -- (30cm,270mm);
\draw[fill,color=orange!10] (-3cm,292.500000mm) rectangle (30cm,277.500000mm);
\node at (0mm,285mm) {core 19};
\draw[color=black!30] (20mm,285mm) -- (30cm,285mm);
\draw[fill,color=orange!10] (-3cm,307.500000mm) rectangle (30cm,292.500000mm);
\node at (0mm,300mm) {core 20};
\draw[color=black!30] (20mm,300mm) -- (30cm,300mm);
\draw[fill,color=orange!10] (-3cm,322.500000mm) rectangle (30cm,307.500000mm);
\node at (0mm,315mm) {core 21};
\draw[color=black!30] (20mm,315mm) -- (30cm,315mm);
\draw[fill,color=orange!10] (-3cm,337.500000mm) rectangle (30cm,322.500000mm);
\node at (0mm,330mm) {core 22};
\draw[color=black!30] (20mm,330mm) -- (30cm,330mm);
\draw[fill,color=orange!10] (-3cm,352.500000mm) rectangle (30cm,337.500000mm);
\node at (0mm,345mm) {core 23};
\draw[color=black!30] (20mm,345mm) -- (30cm,345mm);
\node at (0mm,360mm) {Machine: ziger, topology: badtree};
\node[draw,fill=red!20,minimum size=10mm] (s_0_16) at (50mm,0mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_0_17) at (60mm,0mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_16) at (80mm,240mm) {};
\draw[->,very thick,color=red] (s_0_16.center) -- (r_0_16.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_16_2) at (90mm,240mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_16_1) at (100mm,240mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_0_17) at (90mm,255mm) {};
\draw[->,very thick,color=red] (s_0_17.center) -- (r_0_17.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_17_3) at (100mm,255mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_17_4) at (110mm,255mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_2) at (120mm,30mm) {};
\draw[->,very thick,color=red] (s_16_2.center) -- (r_16_2.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_2_18) at (130mm,30mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_17_3) at (130mm,45mm) {};
\draw[->,very thick,color=red] (s_17_3.center) -- (r_17_3.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_3_13) at (140mm,45mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_3_15) at (150mm,45mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_16_1) at (130mm,15mm) {};
\draw[->,very thick,color=red] (s_16_1.center) -- (r_16_1.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_17_4) at (140mm,60mm) {};
\draw[->,very thick,color=red] (s_17_4.center) -- (r_17_4.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_4_14) at (150mm,60mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_4_12) at (160mm,60mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_2_18) at (150mm,270mm) {};
\draw[->,very thick,color=red] (s_2_18.center) -- (r_2_18.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_18_10) at (160mm,270mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_18_8) at (170mm,270mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_3_13) at (170mm,195mm) {};
\draw[->,very thick,color=red] (s_3_13.center) -- (r_3_13.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_13_5) at (180mm,195mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_4_14) at (180mm,210mm) {};
\draw[->,very thick,color=red] (s_4_14.center) -- (r_4_14.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_3_15) at (180mm,225mm) {};
\draw[->,very thick,color=red] (s_3_15.center) -- (r_3_15.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_4_12) at (190mm,180mm) {};
\draw[->,very thick,color=red] (s_4_12.center) -- (r_4_12.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_18_10) at (190mm,150mm) {};
\draw[->,very thick,color=red] (s_18_10.center) -- (r_18_10.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_10_19) at (200mm,150mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_10_22) at (210mm,150mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_18_8) at (200mm,120mm) {};
\draw[->,very thick,color=red] (s_18_8.center) -- (r_18_8.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_8_21) at (210mm,120mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_8_20) at (220mm,120mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_13_5) at (210mm,75mm) {};
\draw[->,very thick,color=red] (s_13_5.center) -- (r_13_5.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_19) at (230mm,285mm) {};
\draw[->,very thick,color=red] (s_10_19.center) -- (r_10_19.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_19_9) at (240mm,285mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_19_11) at (250mm,285mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_21) at (240mm,315mm) {};
\draw[->,very thick,color=red] (s_8_21.center) -- (r_8_21.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_10_22) at (240mm,330mm) {};
\draw[->,very thick,color=red] (s_10_22.center) -- (r_10_22.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_22_7) at (250mm,330mm) {};
\node[draw,fill=red!20,minimum size=10mm] (s_22_6) at (260mm,330mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_8_20) at (250mm,300mm) {};
\draw[->,very thick,color=red] (s_8_20.center) -- (r_8_20.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_19_9) at (270mm,135mm) {};
\draw[->,very thick,color=red] (s_19_9.center) -- (r_19_9.center); 
\node[draw,fill=red!20,minimum size=10mm] (s_9_23) at (280mm,135mm) {};
\node[draw,fill=blue!20,minimum size=10mm] (r_22_7) at (280mm,105mm) {};
\draw[->,very thick,color=red] (s_22_7.center) -- (r_22_7.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_19_11) at (280mm,165mm) {};
\draw[->,very thick,color=red] (s_19_11.center) -- (r_19_11.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_22_6) at (290mm,90mm) {};
\draw[->,very thick,color=red] (s_22_6.center) -- (r_22_6.center); 
\node[draw,fill=blue!20,minimum size=10mm] (r_9_23) at (310mm,345mm) {};
\draw[->,very thick,color=red] (s_9_23.center) -- (r_9_23.center);

>>>>

\node (core_0_label) at (0mm,0mm) {core 00};
\node (core_1_label) at (0mm,5mm) {core 01};
\node (core_2_label) at (0mm,10mm) {core 02};
\node (core_3_label) at (0mm,15mm) {core 03};
\node (core_4_label) at (0mm,20mm) {core 04};
\node (core_5_label) at (0mm,25mm) {core 05};
\node (core_6_label) at (0mm,30mm) {core 06};
\node (core_7_label) at (0mm,35mm) {core 07};
\node (core_8_label) at (0mm,40mm) {core 08};
\node (core_9_label) at (0mm,45mm) {core 09};
\node (core_10_label) at (0mm,50mm) {core 10};
\node (core_11_label) at (0mm,55mm) {core 11};
\node (core_12_label) at (0mm,60mm) {core 12};
\node (core_13_label) at (0mm,65mm) {core 13};
\node (core_14_label) at (0mm,70mm) {core 14};
\node (core_15_label) at (0mm,75mm) {core 15};
\node (core_16_label) at (0mm,80mm) {core 16};
\node (core_17_label) at (0mm,85mm) {core 17};
\node (core_18_label) at (0mm,90mm) {core 18};
\node (core_19_label) at (0mm,95mm) {core 19};
\node (core_20_label) at (0mm,100mm) {core 20};
\node (core_21_label) at (0mm,105mm) {core 21};
\node (core_22_label) at (0mm,110mm) {core 22};
\node (core_23_label) at (0mm,115mm) {core 23};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_16) at (20mm,0mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_0_17) at (24mm,0mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_16) at (32mm,80mm) {};
\draw[->,semithick,color=red] ($(s_0_16.east)-(1mm,0mm)$) -- ($(r_0_16.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_2) at (36mm,80mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_16_1) at (40mm,80mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_0_17) at (36mm,85mm) {};
\draw[->,semithick,color=red] ($(s_0_17.east)-(1mm,0mm)$) -- ($(r_0_17.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_3) at (40mm,85mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_17_4) at (44mm,85mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_2) at (48mm,10mm) {};
\draw[->,semithick,color=red] ($(s_16_2.east)-(1mm,0mm)$) -- ($(r_16_2.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_2_18) at (52mm,10mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_3) at (52mm,15mm) {};
\draw[->,semithick,color=red] ($(s_17_3.east)-(1mm,0mm)$) -- ($(r_17_3.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_13) at (56mm,15mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_3_15) at (60mm,15mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_16_1) at (52mm,5mm) {};
\draw[->,semithick,color=red] ($(s_16_1.east)-(1mm,0mm)$) -- ($(r_16_1.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_17_4) at (56mm,20mm) {};
\draw[->,semithick,color=red] ($(s_17_4.east)-(1mm,0mm)$) -- ($(r_17_4.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_14) at (60mm,20mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_4_12) at (64mm,20mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_2_18) at (60mm,90mm) {};
\draw[->,semithick,color=red] ($(s_2_18.east)-(1mm,0mm)$) -- ($(r_2_18.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_10) at (64mm,90mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_18_8) at (68mm,90mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_13) at (68mm,65mm) {};
\draw[->,semithick,color=red] ($(s_3_13.east)-(1mm,0mm)$) -- ($(r_3_13.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_13_5) at (72mm,65mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_14) at (72mm,70mm) {};
\draw[->,semithick,color=red] ($(s_4_14.east)-(1mm,0mm)$) -- ($(r_4_14.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_3_15) at (72mm,75mm) {};
\draw[->,semithick,color=red] ($(s_3_15.east)-(1mm,0mm)$) -- ($(r_3_15.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_4_12) at (76mm,60mm) {};
\draw[->,semithick,color=red] ($(s_4_12.east)-(1mm,0mm)$) -- ($(r_4_12.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_10) at (76mm,50mm) {};
\draw[->,semithick,color=red] ($(s_18_10.east)-(1mm,0mm)$) -- ($(r_18_10.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_19) at (80mm,50mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_10_22) at (84mm,50mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_18_8) at (80mm,40mm) {};
\draw[->,semithick,color=red] ($(s_18_8.east)-(1mm,0mm)$) -- ($(r_18_8.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_21) at (84mm,40mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_8_20) at (88mm,40mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_13_5) at (84mm,25mm) {};
\draw[->,semithick,color=red] ($(s_13_5.east)-(1mm,0mm)$) -- ($(r_13_5.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_19) at (92mm,95mm) {};
\draw[->,semithick,color=red] ($(s_10_19.east)-(1mm,0mm)$) -- ($(r_10_19.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_9) at (96mm,95mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_19_11) at (100mm,95mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_21) at (96mm,105mm) {};
\draw[->,semithick,color=red] ($(s_8_21.east)-(1mm,0mm)$) -- ($(r_8_21.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_10_22) at (96mm,110mm) {};
\draw[->,semithick,color=red] ($(s_10_22.east)-(1mm,0mm)$) -- ($(r_10_22.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_22_7) at (100mm,110mm) {};
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_22_6) at (104mm,110mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_8_20) at (100mm,100mm) {};
\draw[->,semithick,color=red] ($(s_8_20.east)-(1mm,0mm)$) -- ($(r_8_20.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_9) at (108mm,45mm) {};
\draw[->,semithick,color=red] ($(s_19_9.east)-(1mm,0mm)$) -- ($(r_19_9.west)+(1mm,0mm)$); 
\node[draw,fill=red!20,minimum width=4mm, minimum height=3mm,anchor=west] (s_9_23) at (112mm,45mm) {};
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_19_11) at (112mm,55mm) {};
\draw[->,semithick,color=red] ($(s_19_11.east)-(1mm,0mm)$) -- ($(r_19_11.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_22_7) at (112mm,35mm) {};
\draw[->,semithick,color=red] ($(s_22_7.east)-(1mm,0mm)$) -- ($(r_22_7.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_22_6) at (116mm,30mm) {};
\draw[->,semithick,color=red] ($(s_22_6.east)-(1mm,0mm)$) -- ($(r_22_6.west)+(1mm,0mm)$); 
\node[draw,fill=blue!20,minimum width=4mm, minimum height=3mm,anchor=west] (r_9_23) at (124mm,115mm) {};
\draw[->,semithick,color=red] ($(s_9_23.east)-(1mm,0mm)$) -- ($(r_9_23.west)+(1mm,0mm)$); 
\begin{pgfonlayer}{background}
\node [fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_18_10) (s_10_19) (s_10_22) (r_4_12) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (r_9_23) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (r_9_23)] (allobjects) {};
\node [draw=black!50,fill=black!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_18_10) (s_10_19) (s_10_22) (r_4_12) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (r_9_23) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (s_0_16) (s_0_17) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_2_18) (s_18_10) (s_18_8) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_13_5) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (r_9_23),scale=1.1] (bg) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_0) at (\x1,0mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_1) at (\x1,5mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_2) at (\x1,10mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_3) at (\x1,15mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_4) at (\x1,20mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_5) at (\x1,25mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_6) at (\x1,30mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_7) at (\x1,35mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_8) at (\x1,40mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_9) at (\x1,45mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_10) at (\x1,50mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_11) at (\x1,55mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_12) at (\x1,60mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_13) at (\x1,65mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_14) at (\x1,70mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_15) at (\x1,75mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_16) at (\x1,80mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_17) at (\x1,85mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_18) at (\x1,90mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_19) at (\x1,95mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_20) at (\x1,100mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_21) at (\x1,105mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_22) at (\x1,110mm) {};
\draw let \p1 = (allobjects.east) in node[] (numa_axis_23) at (\x1,115mm) {};
\node [yscale=0.85,draw=red!50,fill=red!10,fit=(core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_16) (s_0_17) (r_16_2) (s_2_18) (r_16_1) (r_17_3) (s_3_13) (s_3_15) (r_17_4) (s_4_14) (s_4_12) (r_13_5) (numa_axis_0.west) (core_0_label) (core_1_label) (core_2_label) (core_3_label) (core_4_label) (core_5_label) (s_0_16) (s_0_17) (r_16_2) (s_2_18) (r_17_3) (s_3_13) (s_3_15) (r_16_1) (r_17_4) (s_4_14) (s_4_12) (r_13_5) (numa_axis_0.west),rounded corners] {};
\node [yscale=0.85,draw=green!50,fill=green!10,fit=(core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_19_9) (s_9_23) (r_22_7) (r_19_11) (r_22_6) (numa_axis_6.west) (core_6_label) (core_7_label) (core_8_label) (core_9_label) (core_10_label) (core_11_label) (r_18_10) (s_10_19) (s_10_22) (r_18_8) (s_8_21) (s_8_20) (r_19_9) (s_9_23) (r_19_11) (r_22_7) (r_22_6) (numa_axis_6.west),rounded corners] {};
\node [yscale=0.85,draw=blue!50,fill=blue!10,fit=(core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (numa_axis_12.west) (core_12_label) (core_13_label) (core_14_label) (core_15_label) (core_16_label) (core_17_label) (r_0_16) (s_16_2) (s_16_1) (r_0_17) (s_17_3) (s_17_4) (r_3_13) (s_13_5) (r_4_14) (r_3_15) (r_4_12) (numa_axis_12.west),rounded corners] {};
\node [yscale=0.85,draw=orange!50,fill=orange!10,fit=(core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_2_18) (s_18_10) (s_18_8) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_9_23) (numa_axis_18.west) (core_18_label) (core_19_label) (core_20_label) (core_21_label) (core_22_label) (core_23_label) (r_2_18) (s_18_10) (s_18_8) (r_10_19) (s_19_9) (s_19_11) (r_8_21) (r_10_22) (s_22_7) (s_22_6) (r_8_20) (r_9_23) (numa_axis_18.west),rounded corners] {};
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,0mm) -- (\x2,0mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,5mm) -- (\x2,5mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,10mm) -- (\x2,10mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,15mm) -- (\x2,15mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,20mm) -- (\x2,20mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,25mm) -- (\x2,25mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,30mm) -- (\x2,30mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,35mm) -- (\x2,35mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,40mm) -- (\x2,40mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,45mm) -- (\x2,45mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,50mm) -- (\x2,50mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,55mm) -- (\x2,55mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,60mm) -- (\x2,60mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,65mm) -- (\x2,65mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,70mm) -- (\x2,70mm);
\draw[color=black!30] let \p1 = (core_10_label.east), \p2 = (allobjects.east) in (\x1,75mm) -- (\x2,75mm);
